### 2019-05-22 2-Chapters/2-Chapter/chapter2.tex
My thesis is so long, and so stupid
Thanks Christophe for comments on Ch2
On se fait jeter dehors !

% First chapter begins here
\chapter{The Stochastic Multi-Armed Bandits Model}
\label{chapter:2}
\minitoc

@@

\paragraph{Publication.}
%
Section~\ref{sec:2:chooseYourPreferredBanditAlgorithm} in this chapter is based on the article \cite{Besson2018WCNC}.

@@

\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/2-Chapter/Images/}}

@@

\tikzstyle{block} = [align=center, draw, fill=gray!25, rectangle, minimum height=3em, minimum width=6em]
\begin{figure}[h!]
    \centering
    \resizebox{0.350\textwidth}{!}{
        \begin{tikzpicture}[auto, node distance=5cm, >=latex]
            %
            % We start by placing the blocks
            \node [block] (player) at (0,0) {Player};
            % We draw an edge between the player and system block to
            \node [block] (environment) at (4,0) {MAB problem};
            % Once the nodes are placed, connecting them is easy.
            \draw [->] (player) to[bend left=90] node[pos=0.5] {Chooses a discrete action $k=A(t) \in\{1,\dots,K\}$} (environment);
            \draw [->] (environment) to[bend left=90] node[pos=0.5] {Observes a real-valued reward $r_k(t) \in \R$} (player);
            %
        \end{tikzpicture}
    }
\caption{Reinforcement learning cycle in a MAB model, for time steps $t=1,\dots,T$.}
\label{fig:2:ReinforcementLearningCycleMABmodel}
\end{figure}

@@

\paragraph{An interactive demo to discover the MAB problem (for the novice).}
%
If you are discovering the concept of bandit model here, I would like to recommend you to go online and play a few times with an interactive demonstration.
On this demo, you will be facing a MAB problem with $K=5$ arms, and you have $T=100$ decisions to make.
The demo is hosted on my website, at \href{https://perso.crans.org/besson/phd/MAB\_interactive\_demo/}{\texttt{perso.crans.org/besson/phd/MAB\_interactive\_demo/}}, and illustrated below.

@@

\paragraph{On one-dimensional exponential family.}
%
% On one-dimensional exponential family...

@@

-- A second important result is a simplified form for the \emph{Kullback-Leibler divergence} \cite{KullbackLeibler51}, for two distributions lying in the same exponential family.
The KL divergence between two distributions $d_1=\Pr(x|\eta_1)$ and $d_2=\Pr(x|\eta_2)$ is defined as
\begin{equation}\label{eq:2:Kullback-LeiblerDivergenceExpFamily1}
    \KL\left(\Pr(x|\eta_1), \Pr(x|\eta_2)\right) = \int \Pr(x|\eta_1) \log\left(\frac{\Pr(x|\eta_1)}{\Pr(x|\eta_1)}\right) \lambda(\mathrm{d}x) = \E_{d_1} \left[ \log\left(\frac{\Pr(x|\eta_1)}{\Pr(x|\eta_1)}\right) \right].
\end{equation}
%
So this KL divergence can be written $\KL( \eta_1, \eta_2 ) = \KL(\Pr(x|\eta_1), \Pr(x|\eta_2))$, and it can be simplified to an expression using only the two parameters $\eta_1$ and $\eta_2$,
and $\mu_1 = \E_{\eta_1}[X]$ the mean of distribution $d_1$:
%
\begin{equation}\label{eq:2:Kullback-LeiblerDivergenceExpFamily2}
    \KL\left( \eta_1, \eta_2 \right) = \E_{d_1}[ (\eta_1 - \eta_2) X ] - A(\eta_1) + A(\eta_2) = (\eta_1 - \eta_2) \mu_1 - A(\eta_1) + A(\eta_2),
\end{equation}

Without diving more in the details of exponential families,
it is interesting to illustrate this definition and the notations with two important examples:
%
\begin{itemize}
    \item
    \textbf{Bernoulli distributions} can be seen as an exponential family with $h(x) = 1$,
    and for a Bernoulli distribution of mean $\mu\in[0,1]$,
    the parameter is $\eta = \mu / (1 - \mu)$, giving $A(\eta) = \log(1 + \mathrm{e}^{\eta})$
    (with the limit behavior $\eta=+\infty$ if $\mu=0$).

    \item
    \textbf{Gaussian distributions} of a fixed variance are a one-dimensional exponential family,
    and in this thesis we do not consider Gaussian with an unknown variance.
    For a variance of $\sigma^2$, the family uses
    % $T(x) = [x ; x^2]^T$ and
    $h(x) = 1/\sqrt{2\pi\sigma^2} \exp(-x^2/(2\sigma^2))$,
    and for a Gaussian distribution with mean $\mu\in\R$ (\ie, $\cN(\mu,\sigma^2)$),
    the parameter is $\eta = \mu/\sigma^2$, giving $A(\eta) = \mu^2/(2\sigma^2)$
    (see Chapter~8 of \cite{JordanCourseStatBerkeley}).
    % % For a generic variance,
    % This shows that the Gaussian distributions
    % % are a two-dimensional exponential families,
    % with a fixed variance $\sigma^2$ form indeed a one-dimensional exponential family.
\end{itemize}

In the rest of this thesis, \emph{we only consider bounded rewards in the mathematical developments}, and we mostly focus on Bernoulli distributions.
First, we restrict for simplicity to Bernoulli distributions for the simulations shown in Chapter~\ref{chapter:3}, even if our library does implement all the distributions commonly found in the literature (including unbounded one-dimensional exponential families and even Markov models).
% Then in Chapter~\ref{chapter:4}, each static IoT device in the noisy environment is assumed to be following a Bernoulli emission pattern in a fixed channel, FIXME
%
For example when we study multi-player bandits in Chapter~\ref{chapter:5}, for the model without sensing, we explain that restricting to the Bernoulli case is interesting and it is actually the hardest one, as continuous distributions with a null mass on $r(t)=0$ yield a much simpler problem.
%
Finally, in Chapter~\ref{chapter:6} we analyze our proposed algorithm in the setting on bounded distributions, without restricting to Bernoulli distributions, but we use the fact that bounded distributions on $[0,1]$ are sub-Bernoulli, and we use Bernoulli Kullback-Leibler divergences in our analysis.

@@

% ----------------------------------------------------------------------------
\section{Applications of stochastic MAB}
\label{sec:2:applicationsofStochasticMAB}

@@

The focus of this work is on cognitive radio and IoT networks, where arms can represent wireless orthogonal channels, but more generally any resource characterizing the communication between a wireless device and a gateway (\eg, spreading factor for LoRa \cite{KerkoucheAlami18}, power allocation for NOMA etc ). In cognitive radio using centralized supervision, for instance if the gateway can decide the allocation of devices to resources, MAB can also be used to let the gateway explore different allocations and learn by itself a good allocation, see for instance this article that consider 5G-like networks with small cells \cite{Maghsudi16}.

@@

If the goal of the player is to maximize $\E[\sum_{t=1}^T r_{A(t)}(t)]$,
the optimal strategy for this bandit problem is to always pull an optimal arm, but of course it is unrealistic as the player does not know the true means and cannot know which arm is optimal.
%
Comparing the difference between the performance of a fixed baseline and that of the player is a common approach in machine learning research,
and here we can compare with the oracle strategy that obtains an (expected) reward of $\mu^*$ at each time step.
%
For a fixed horizon $T$, if $k^*$ denotes the index of any optimal arm,
let us introduce the (mean) regret $R_T^{\cA}$ of an algorithm $\cA$ as
\[ R_T^{\cA} = \E\left[ \sum_{t=1}^T r_{k^*}(t) - r_{A(t)}(t) \right]. \]
%
We can rewrite this expression to obtain the following definition of the regret:
$R_T^{\cA}$
$= \E\left[ \sum_{t=1}^T r_{k^*}(t) \right] - \E\left[ \sum_{t=1}^T r_{A(t)}(t) \right]$
$= T \E\left[ r_{k^*}(1) \right] - \sum_{t=1}^T \E\left[ r_{A(t)}(t) \right]$
$= T \mu^* - \sum_{t=1}^T \E\left[ r_{A(t)}(t) \right]$.
% This is the definition we give below.

@@

Such decomposition of the regret is useful for at least two reasons.
%
On the first hand, from a numerical simulation point-of-view, when we run a finite number of repetitions of the same stochastic experiment, if one wants to compute and visualize the regret, she can either use the definition with the rewards, or the decomposition and simply sum the gaps $\Delta_k$ with the number of sub-optimal draws.
Mathematically, both quantities are equal in expectation, but with only a finite number of trajectories and observations, the first estimate is more noisy than the second one, since the randomness on the rewards is (partially) removed.
In our library SMPyBandits, we implement both possibilities, and all values of regret used in this thesis are based on the second estimator, using the decomposition of Lemma~\ref{lem:2:RegretDecomposition}, because it gives smoother curves and faster convergence to the limit behavior.
%
On the second hand, this decomposition is necessary as theoretical analyses of the regret of MAB algorithms are usually based on controlling the suboptimal draws $N_k(T$ and not directly the regret $R_T^{\cA}$.
For example, we extend this decomposition to the multi-player case in Chapter~\ref{chapter:3}, in Lemma~\ref{lem:5:DecompositionRegret}, and as it also uses the draws $N_k(T)$, it is the first quantity we prove to be bounded by $\bigO{\log(T)}$ when we prove the regret upper-bound of our proposal \MCTopM-\klUCB.

@@

In all this section, we restrict to stationary stochastic bandits with $K\geq2$ arms.
We do not give proofs of the following theorems, as they can be found in the historical papers, and simpler proofs are given in recent references, such as \cite{Bubeck12}, \cite{LattimoreBanditAlgorithmsBook}, or Chapter~2 in \cite{Slivkins2019} for instance.

Let $\cI$ denote the set of all problem instances, with $K \geq 2$ arms whose rewards lie in $[0,1]$ (and no other hypothesis).
To specify the dependency on an instance $I$, we denote the regret of $\cA$ on instance $I$ and horizon $T$ by $R_T^{\cA}(I)$.

@@

\subsection{Summary of classification of the most famous algorithms}

A huge table in one page in portrait mode, giving:
- name
- reference, year
- family, classification
- time/memory complexity ?
- regret bound for stochastic regret

of about 20/30 algorithms?

@@

\subsection{Naive approach: use UCB or Thompson sampling, and forget about the rest!}
First solution: be naive, only use UCB everywhere

\subsection{Use prior knowledge about the future application to select beforehand the chosen algorithm}
Second solution, if one has some prior knowledge about the domain or setting for which the learning algorithms will be deployed, she can run synthetic or real-world simulations, compare many algorithms before deployment, and select the best algorithm!

@@

The first contribution of this manuscript \cite{Besson2018WCNC} concluded this chapter, in Section~\ref{sec:2:chooseYourPreferredBanditAlgorithm}. We tackle the question of how to select a particular bandit algorithm when a practitioner is facing a particular (unknown) bandit problem.
Instead of always choosing a fixed algorithm, or running costly benchmarks before real-world deployment of the chosen algorithm, we advise to select a few candidate algorithms, where at least one is expected to be very efficient for the given problem, and use online algorithm selection to automatically and dynamically decide the best candidate.
We proposed an extension of the Exp4 algorithm for this problem, \Aggr, and illustrate its performance on some bandit problems.
%
The numerical simulations used our Python open-source library, SMPyBandits, that is presented in details in the next Chapter~\ref{chapter:3}.
The next chapter also includes simulations of the most important MAB algorithms that we presented above, on Bernoulli distributed problems of various sizes and durations.

@@

% \subsection{Efficient numerical computation of Kullback-Leibler divergences and \klUCB{} indexes}

% \TODOL{On s'en fout en fait de ça, non ? Ma thèse n'a pas étudiée klUCB, et les implémentations en C ne sont pas de moi mais viennent de pymaBandits... Donc inutile de parler de ça !}

% I want to detail the maths behind an implementation of klUCB, see https://smpybandits.github.io/docs/Policies.kullback.html and all what is detailed there.

% How to write a fast version of klBern and klucbBern (the two most used functions), using C or Numba or Cython, maybe I can include the speed up simulations here? First piece of code, before really presenting SMPyBandits ?

% My work for this part is also published on https://github.com/Naereen/Kullback-Leibler-divergences-and-kl-UCB-indexes
% (in Python) and https://github.com/Naereen/KullbackLeibler.jl (in Julia).

>>>>

% First chapter begins here
\chapter{The Stochastic Multi-Armed Bandits Model}
\label{chapter:2}
\minitoc
% Write miniTOC just after the title
\graphicspath{{2-Chapters/2-Chapter/Images/}}

@@

\paragraph{Publication.}
%
The Section~\ref{sec:2:chooseYourPreferredBanditAlgorithm} in this chapter is based on the article \cite{Besson2018WCNC}.

@@

% \newpage

@@

\tikzstyle{block} = [align=center, draw, fill=gray!25, rectangle, minimum height=3em, minimum width=6em]
\begin{figure}[h!]
    \centering
    \resizebox{0.50\textwidth}{!}{
        \begin{tikzpicture}[auto, node distance=5cm, >=latex]
            %
            % We start by placing the blocks
            \node [block] (player) at (0,0) {Player};
            % We draw an edge between the player and system block to
            \node [block] (environment) at (4,0) {MAB problem};
            % Once the nodes are placed, connecting them is easy.
            \draw [->] (player) to[bend left=90] node[pos=0.5] {Chooses a discrete action $k=A(t) \in\{1,\dots,K\}$} (environment);
            \draw [->] (environment) to[bend left=90] node[pos=0.5] {Observes a real-valued reward $r_k(t) \in \R$} (player);
            %
        \end{tikzpicture}
    }
\caption{Reinforcement learning cycle in a MAB model, for time steps $t=1,\dots,T$.}
\label{fig:2:ReinforcementLearningCycleMABmodel}
\end{figure}

@@

\paragraph{An interactive demo to discover the MAB problem (for the novice).}
\label{par:2:interactiveDemoDiscoverMAB}
%
If you are discovering the concept of bandit model here, I would like to recommend you to go online and play a few times with an interactive demonstration.
On this demo, you will be facing a MAB problem with $K=5$ arms, and you have $T=100$ decisions to make.
The demo is hosted on my website, at \href{https://perso.crans.org/besson/phd/MAB\_interactive\_demo/}{\texttt{perso.crans.org/besson/phd/MAB\_interactive\_demo/}}, and illustrated below.

@@

\paragraph{We restrict to one-dimensional exponential family.}
%
% On one-dimensional exponential family...

@@

-- A second important result is a simplified form for the \emph{Kullback-Leibler divergence} \cite{KullbackLeibler51}, for two distributions lying in the same exponential family.
The KL divergence is also called the relative entropy is a measure of how one probability distribution is different from a second, reference probability distribution.

\begin{defn}[Kullback-Leibler divergence]\label{def:2:KLDivergence}
    The KL divergence between two distributions $d_1$ and $d_2$ is defined as
    \begin{equation}\label{eq:2:Kullback-LeiblerDivergenceExpFamily1}
        \KL\left(d_1, d_2\right) = \int d_1 \log\left(\frac{d_2}{d_1}\right) \lambda(\mathrm{d}x) = \E_{d_1} \left[ \log\left(\frac{d_2}{d_1}\right) \right].
    \end{equation}
\end{defn}

Following this Definition~\ref{def:2:KLDivergence} for two distributions
$d_1=\Pr(x|\eta_1)$ and $d_2=\Pr(x|\eta_2)$,
we can write $\KL( \eta_1, \eta_2 ) = \KL(\Pr(x|\eta_1), \Pr(x|\eta_2))$, which can be simplified to use only the two parameters $\eta_1$ and $\eta_2$,
and $\mu_1 = \E_{\eta_1}[X]$ the mean of distribution $d_1$:
%
\begin{equation}\label{eq:2:Kullback-LeiblerDivergenceExpFamily2}
    \KL\left( \eta_1, \eta_2 \right) = \E_{d_1}[ (\eta_1 - \eta_2) X ] - A(\eta_1) + A(\eta_2) = (\eta_1 - \eta_2) \mu_1 - A(\eta_1) + A(\eta_2),
\end{equation}

Without diving more in the details of exponential families,
it is interesting to illustrate this definition and the notations with two important examples:
%
\begin{itemize}
    \item
    \textbf{Bernoulli distributions} can be seen as an exponential family with $h(x) = 1$,
    and for a Bernoulli distribution of mean $\mu\in[0,1]$, denoted $B(\mu)$,
    the parameter is $\eta = \mu / (1 - \mu)$, giving $A(\eta) = \log(1 + \mathrm{e}^{\eta})$
    (with the limit behavior $\eta=+\infty$ if $\mu=0$).
    %
    Moreover, the KL divergence between $B(x)$ and $B(y)$, of parameters $\eta$, $\eta'$ is given by
    $\kl(x,y) = \KL_{B}(\eta,\eta') = x \log(x/y) + (1-x) \log((1-x)/(1-y))$.

    \item
    \textbf{Gaussian distributions} of a fixed variance are a one-dimensional exponential family,
    and in this thesis we do not consider Gaussian with an unknown variance.
    For a variance of $\sigma^2$, the family uses
    % $T(x) = [x ; x^2]^T$ and
    $h(x) = 1/\sqrt{2\pi\sigma^2} \exp(-x^2/(2\sigma^2))$,
    and for a Gaussian distribution with mean $\mu\in\R$, denoted $\cN(\mu,\sigma^2)$,
    the parameter is $\eta = \mu/\sigma^2$, giving $A(\eta) = \mu^2/(2\sigma^2)$
    (see Chapter~8 of \cite{JordanCourseStatBerkeley}).
    % % For a generic variance,
    % This shows that the Gaussian distributions
    % % are a two-dimensional exponential families,
    % with a fixed variance $\sigma^2$ form indeed a one-dimensional exponential family.
    %
    Moreover, the KL divergence between $\cN(x,\sigma^2)$ and $\cN(x,\sigma^2)$, of parameters $\eta$, $\eta'$ is given by
    $d(x,y) = \KL_{\cN}(\eta,\eta') = (x-y)^2 / (2\sigma^2)$.
\end{itemize}

In the rest of this thesis, \emph{we only consider bounded rewards in the mathematical developments}, and we mostly focus on Bernoulli distributions, because they are usually the most relevant choice for the application of choice.
First, we restrict for simplicity to Bernoulli distributions for the simulations shown in Chapter~\ref{chapter:3}, even if our library does implement all the distributions commonly found in the literature (including unbounded one-dimensional exponential families and even Markov models).
% Then in Chapter~\ref{chapter:4}, each static IoT device in the noisy environment is assumed to be following a Bernoulli emission pattern in a fixed channel, FIXME
%
For example when we study multi-player bandits in Chapter~\ref{chapter:5}, for the model without sensing, we explain that restricting to the Bernoulli case is interesting and it is actually the hardest one, as continuous distributions with a null mass on $r(t)=0$ yield a much simpler problem.
%
Finally, in Chapter~\ref{chapter:6} we analyze our proposed algorithm in the setting on bounded distributions, without restricting to Bernoulli distributions, but we use the fact that bounded distributions on $[0,1]$ are sub-Bernoulli, and we use the Bernoulli Kullback-Leibler divergence in our analysis.

@@

% ----------------------------------------------------------------------------
\section{Different applications of stochastic MAB}
\label{sec:2:applicationsofStochasticMAB}

@@

The focus of this work is on cognitive radio and IoT networks, where arms can represent wireless orthogonal channels, but more generally any resource characterizing the communication between a wireless device and a gateway (\eg, spreading factor for LoRa \cite{KerkoucheAlami18}, power allocation for NOMA etc). In cognitive radio using centralized supervision, for instance if the gateway can decide the allocation of devices to resources, MAB can also be used to let the gateway explore different allocations and learn by itself a good allocation, see for instance this article that consider 5G-like networks with small cells \cite{Maghsudi16}.

@@

If the goal of the player is to maximize $\E\left[\sum_{t=1}^T r_{A(t)}(t)\right]$,
the optimal strategy for this bandit problem is to always pull an optimal arm, but of course it is unrealistic as the player does not know the true means and cannot know which arm is optimal.
%
Comparing the difference between the performance of a fixed baseline and that of the player is a common approach in machine learning research,
and here we can compare with the oracle strategy that obtains an (expected) reward of $\mu^*$ at each time step.
%
For a fixed horizon $T$, if $k^*$ denotes the index of any optimal arm,
let us introduce the (mean) regret $R_T^{\cA}$ of an algorithm $\cA$ as
\[ R_T^{\cA} = \E\left[ \sum_{t=1}^T r_{k^*}(t) - r_{A(t)}(t) \right]. \]
%
We can rewrite this expression to obtain the following definition of the regret:
$R_T^{\cA}$
$= \E\left[ \sum_{t=1}^T r_{k^*}(t) \right] - \E\left[ \sum_{t=1}^T r_{A(t)}(t) \right]$
$= T \E\left[ r_{k^*}(1) \right] - \sum_{t=1}^T \E\left[ r_{A(t)}(t) \right]$
$= T \mu^* - \sum_{t=1}^T \E\left[ r_{A(t)}(t) \right]$.
% This is the definition we give below.

@@

\textbf{Applications:}
%
Such decomposition of the regret is useful for at least two reasons.
%
On the first hand, from a numerical simulation point-of-view, when we run a finite number of repetitions of the same stochastic experiment, if one wants to compute and visualize the regret, she can either use the definition with the rewards, or the decomposition and simply sum the gaps $\Delta_k$ with the number of sub-optimal draws.
Mathematically, both quantities are equal in expectation, but with only a finite number of trajectories and observations, the first estimate is more noisy than the second one, since the randomness on the rewards is (partially) removed.
In our library SMPyBandits, we implement both possibilities, and all values of regret used in this thesis are based on the second estimator, using the decomposition of Lemma~\ref{lem:2:RegretDecomposition}, because it gives smoother curves and faster convergence to the limit behavior.
%
On the second hand, this decomposition is necessary as theoretical analyses of the regret of MAB algorithms are usually based on controlling the suboptimal draws $N_k(T)$ and not directly the regret $R_T^{\cA}$.
For example, we extend this decomposition to the multi-player case in Chapter~\ref{chapter:3}, in Lemma~\ref{lem:5:DecompositionRegret}, and as it also uses the draws $N_k(T)$, it is the first quantity we prove to be bounded by $\bigO{\log(T)}$ when we prove the regret upper-bound of our proposal \MCTopM-\klUCB.

@@

In all this section, we restrict to stationary stochastic problems with $K\geq2$ arms.
We do not give proofs of the following theorems, as they can be found in the historical papers, and simpler proofs are given in recent references, such as \cite{Bubeck12}, \cite{LattimoreBanditAlgorithmsBook}, or Chapter~2 in \cite{Slivkins2019} for instance.
%
Let $\cI$ denote the set of all problem instances, with $K \geq 2$ arms whose rewards lie in $[0,1]$ (and no other hypothesis).
To specify the dependency on an instance $I$, we denote the regret of $\cA$ on instance $I$ and horizon $T$ by $R_T^{\cA}(I)$.

@@

% \subsection{Summary of classification of the most famous algorithms}

% A huge table in one page in portrait mode, giving:
% - name
% - reference, year
% - family, classification
% - time/memory complexity ?
% - regret bound for stochastic regret

% of about 20/30 algorithms?

@@

For any real-world applications of MAB algorithms,
several solutions have been explored based on various models.
Thus, when a practitioner is facing a problem where MAB algorithms could be used, it is not an easy task to decide which model and which algorithms to use.
It is hard to predict which solution could be the best for real-world conditions at every instants,
and even by assuming a stationary environment, when one is facing a certain problem but has limited information about it, it is hard to know beforehand which algorithm can be the best solution.

In this Section, we first present two naive approaches for selecting an algorithm when facing a new problem, then we detail the online approach that uses a ``master'' MAB algorithm running on top of a pool of ``followers'' algorithms, and we present our contribution that is a new ``master'' algorithm based on \ExpQ.
This section is based on our article \cite{Besson2018WCNC}.

% ----------------------------------------------------------------------
\subsection{Motivation for online algorithm selection}\label{sub:25:introduction}

Many different learning algorithms have been proposed by the machine learning community,
and most of them depend on several parameters, for instance $\alpha$ for \UCB, the prior for Thompson sampling or BayesUCB,
the $\kl$ function for \klUCB{} etc.
Every time a new MAB algorithm $\Alg$ is introduced, it is compared and benchmarked on some bandit instance, parameterized by $\boldsymbol{\mu} = (\mu_1,\dots,\mu_K)$, usually by focusing on its expected regret $R_T = \E_{\boldsymbol{\mu}}[\widetilde{R_T}]$.
%
For a known and specific instance, simulations help to select the best algorithm in a pool of algorithms.
But when one wants to tackle an \emph{unknown} real-world problem, one expects to be efficient against \emph{any} problem, of any kind, size and complexity:
ideally one would like to use an algorithm that can be applied identically against any problem.

\paragraph{Naive approaches.}
%
On the first hand, a practitioner can decide to pick one algorithm, maybe because it seems efficient on other problems, or because it is simple enough to be used in its application. For instance, it can be hard to implement complicated algorithms on limited hardware such as embedded chips in a very low-cost IoT end-device, and so a practitioner could chose to only consider the \UCB{} algorithm (or other low-cost algorithm).
%
On the other hand, if prior knowledge on the application at hand is available, one could implement some benchmarks, and compare a set of algorithms on different problems. If a leader appears clearly, it is then possible to choose it for the application.

\paragraph{Small example.}
%
For instance, if you know that the considered problem can either have $K$ arms with very close means, or one optimal arm far away from the other, two versions of a \UCB{} algorithms will perform quite differently in the two problems:
using a large $\alpha$, \ie, favoring exploration, will give low regret in the first case,
while using a low $\alpha$, \ie, favoring exploitation, will give low regret in the second case.
One approach can be to use an intermediate value, as $\alpha=1/2$ suggested by theory, but another approach could be to consider an aggregated vote of different versions of \UCB, each running with a different value of $\alpha$ (\eg, in a logarithmic grid), and let another learning algorithm decide which value of $\alpha$ is the best for the problem at hand.

\paragraph{The online approach.}
%
Another possibility is to consider an online approach, which is interested in the case where the computation power or memory storage of the application is not a limitation factor, but where one cannot run benchmarks before deploying the application.
We consider a fixed set of algorithms, and we use another learning algorithm on top of this set, to learn \emph{on the fly} which one should be trusted more, and eventually, used on its own.

The aggregation approach is especially interesting if we know that the problem the device will face is one of a few known kinds of problems.
In such cases, if there is $N$ different sorts of problems, and if one has prior knowledge on it, one can use the naive approach to select an algorithm $\cA_i$ which should perform well on problem $i$, for $i\in[N]$,
and use the aggregation of $\cA_1,\dots,\cA_N$ when facing the unknown problem.

% To choose the best algorithm, three approaches can be followed:
% \begin{itemize}
%     \item
% \end{itemize}
% either extensive benchmarks are done beforehand -- if this is possible -- to select the algorithm and its optimal parameters, or an adaptive algorithm is used to learn \emph{on the fly} its parameters.

% We present a simple adaptive solution, that aggregates several learning algorithms in parallel and adaptively chooses which one to trust the most.

% \paragraph{Outline}
% This section is organized as follows.
% First, we explain in Section~\ref{sub:25:aggregation} how to combine such algorithms for aggregation.
% Then we present our proposed algorithm, called \Aggr, in Section~\ref{sub:25:Aggr},
% Finally, we present numerical experiments in Section~\ref{sub:25:numExp},
% on Bernoulli and non-Bernoulli MAB problems,
% comparing the regret of several algorithms against different aggregation algorithms.
% Theoretical guarantees are shortly discussed in Section~\ref{sub:25:theory}, and Section~\ref{sub:25:conclusion} concludes.

% \subsection{Naive approaches}

% As mentioned, there are two naive approaches

% use UCB or Thompson sampling, and forget about the rest!}
% First solution: be naive, only use UCB everywhere

% \subsection{Use prior knowledge about the future application to select beforehand the chosen algorithm}

% Second solution, if one has some prior knowledge about the domain or setting for which the learning algorithms will be deployed, she can run synthetic or real-world simulations, compare many algorithms before deployment, and select the best algorithm!

@@

The first contribution of this manuscript concludes this chapter, in Section~\ref{sec:2:chooseYourPreferredBanditAlgorithm}, and corresponds to our article \cite{Besson2018WCNC}.
We tackle the question of how to select a particular bandit algorithm when a practitioner is facing a particular (unknown) bandit problem.
Instead of always choosing a fixed algorithm, or running costly benchmarks before real-world deployment of the chosen algorithm, we advise to select a few candidate algorithms, where at least one is expected to be very efficient for the given problem, and use online algorithm selection to automatically and dynamically decide the best candidate.
We proposed an extension of the Exp4 algorithm for this problem, \Aggr, and illustrate its performance on some bandit problems.
%
The numerical simulations used our Python open-source library, SMPyBandits, that is presented in details in the next Chapter~\ref{chapter:3}.
The next chapter also includes simulations of the most important MAB algorithms that we presented above, on Bernoulli distributed problems of various sizes and durations.

@@
